INTELLIGENT SYSTEMS

### 2021-04-10 slides.tex
finish slide paper5

\begin{frame}{EXPERIMENTS AND RESULTS}

@@

\end{document}

>>>>

\begin{frame}{EXPERIMENTS AND RESULTS - Gait recognition}

@@

\begin{frame}{EXPERIMENTS AND RESULTS - Authentication}
    For identity authentication, on the other hand, the results shown in the table show that for this type of problem the single task model is better than the multi-task model. This happens because in this problem a single label (id) is required and not others. The introduction of other labels leads the multitask model to have worse accuracy than the single task model. The indices AUC (higher is better) and EER (lower is better) are calculated thanks to the probabilities obtained from the Euclidean distance vector.
    \begin{table}[h!]
        \centering
        \begin{adjustbox}{max width=\textwidth}
        \begin{tabular}{|c|cc|}
            \hline
            Architecture & EER & AUC\\
            \hline
            SingleTask Accelerometer & 1.47 & 99.91\\
            SingleTask Gyroscope & 2.50 & 99.80\\
            \hline
            MultiTask Accelerometer & 1.61 & 99.90\\
            MultiTask Gyroscope & 2.85 & 99.72\\
            \hline
            SingleTask Fusion & \bfseries{1.14} & \bfseries{99.93}\\
            \hline
            MultiTask Fusion & 1.34 & 99.92\\
            \hline
        \end{tabular}
        \end{adjustbox}
        \caption{Authentication accuracy.}
        \label{Authentication}
    \end{table}
\end{frame}

\begin{frame}{EXPERIMENTS AND RESULTS - State of the art Comparison}
    Comparing the proposed system with those already existing in the state 
    of the art, both for recognition and authentication, the performance, in 
    terms of accuracy, achieved outperforms those competitors.
        \begin{minipage}{\linewidth}
        \centering
        \begin{minipage}{0.45\linewidth}
            \begin{table}[h!]
                \centering
                \begin{adjustbox}{max width=\textwidth}
                \begin{tabular}{|c|ccc|c|}
                    \hline
                    CNN & Id & Age & Gender & Avg\\
                    \hline
                    AE-GDI-CC & 61.0 & - & - & -\\
                    Muaaz et al. & 63.5 & - & - & -\\
                    Ngo et al. & 70.2 & - & - & -\\
                    Wei et al. & 83.8 & - & - & - \\
                    \hline
                    MultiTask Fusion & \bfseries{94.8} & \bfseries{96.1} & \bfseries{97.7} & \bfseries{96.2}\\
                    \hline
                \end{tabular}
                \end{adjustbox}
                \caption{Gait recognition comparison with some methods.}
                \label{Gait comparison}
            \end{table}
        \end{minipage}
        \hspace{0.05\linewidth}
        \begin{minipage}{0.45\linewidth}
            \begin{table}[h!]
                \centering
                \begin{adjustbox}{max width=\textwidth}
                \begin{tabular}{|c|c|}
                    \hline
                    Approach & EER\\
                    \hline
                    Gafurov et al. & 15.8 \\
                    Derawi et al. & 14.3 \\
                    Rong et al. & 14.3 \\
                    Ngo et al. & 13.5 \\
                    Imp GDI + i-vector & 7.1 \\
                    NC GDI + i-vector & 5.6 \\
                    \hline
                    SingleTask Fusion & \bfseries{1.1}\\
                    \hline
                \end{tabular}
                \end{adjustbox}
                \caption{Authentication comparison with some methods.}
                \label{Authentication comparison}
            \end{table}
        \end{minipage}
    \end{minipage}
\end{frame}

\begin{frame}{CONCLUSIONS}
    As a final consideration, the model to be used, in the case of gait recognition, 
    is the one that merges the input information and adopts a multitask 
    approach. On the other hand, as regards the authentication problem, it has 
    been seen that it is better to use a singletask model.
\end{frame}
\end{document}
